paper3

### 2022-09-01 paper3.Rmd
2nd Sep

# -- spatial join OSGB 1 km grid with Scenic-Or-Not data
test <- st_join(grid_1km, sc)

test1 <- test |>
  aggregate(cbind(ID,
                  `Geograph URI`,
                  Votes,
                  Number,
                  Mean,
                  Median,
                  BayeScore,
                  Entropy,
                  Variance)~PLAN_NO, data = ., paste0, collapse = ",") %>%
  merge(LANDMAP, ., by = "UID", all = T) %>%
  as_tibble()

>>>>

# -- spatial join OSGB 1 km grid with Scenic-Or-Not data
test <- st_join(grid_1km, sc) 
library(dplyr)

test1 <- test |>
  st_drop_geometry() |>
  group_by(PLAN_NO) |>
  summarise(ID = paste2(ID, collapse = ', '),
            `Geograph URI` = paste(`Geograph URI`, collapse = ', '),
            Votes = paste(Votes, collapse = ', '),
            Number = paste(Number, collapse = ', '),
            Mean = paste(Mean, collapse = ', '),
            Median = paste(Median, collapse = ', '),
            BayeScore = paste(BayeScore, collapse = ', '),
            Entopy = paste(Entropy, collapse = ', ')) |>
  ungroup() |>
  rowwise() |>

test2 <- test1 |>  
  mutate(Photos = strsplit(ID, ',') |> unlist() |> !is.na() |> length())

strsplit(",") %>% unlist() %>% as.numeric() %>% mean()

data %>% 
      group_by(foo) %>% 
      mutate(bars_by_foo = paste0(bar, collapse = ""))

# library(dplyr)
# df %>% 
#   group_by_(~page, ~passage, ~person) %>%
#   summarize_(text=~paste(text, collapse=' '))

  aggregate(#cbind(# ID,
                  # `Geograph URI`,
                  # Votes,
                  # Number,
                  # Mean,
                  # Median,
                  # BayeScore,
                  # Entropy,
                  Variance~PLAN_NO, data = ., FUN = paste, collapse = ",") %>%
  merge(grid_1km, ., by = "PLAN_NO", all = T) |>
  as_tibble()
